### 2018-09-05 Sections/essay_quantcoin.tex
Some proof-reading

Consider the time-share future contract model as a basis for a currency. Unlike fiat currency, this monetary system would not be inflationary since the commodity backing the currency is one which cannot be easily counterfeited -- the only way to make more currency is to provide more genuine, functional, online qubits, which increases the money supply over time in tandem with the underlying asset backing it. This would in effect be a full-reserve banking system\index{Full-reserve banking}, where the direct one-to-one convertability between currency (forward contracts on computation) and its backing asset (time-shared access to physical qubits) eliminates the money multiplier\index{Money multiplier}, a system essentially immune to bank runs\index{Bank runs}.

>>>>

Consider the time-share future contract model as a basis for a currency. Unlike fiat currency, this monetary system would not be inflationary since the commodity backing the currency is one which cannot be easily counterfeited -- the only way to make more currency is to provide more genuine, functional, online qubits, which increases the money supply over time in tandem with the underlying asset backing it. This would in effect be a full-reserve banking system\index{Full-reserve banking}, where the direct one-to-one convertibility between currency (forward contracts on computation) and its backing asset (time-shared access to physical qubits) eliminates the money multiplier\index{Money multiplier}, a system essentially immune to bank runs\index{Bank runs}.

### 2018-09-05 Sections/essay_the_economics_of_the_quantum_internet.tex
Some proof-reading

A key question regarding the economics of the quantum internet is the extent to which it will be able to piggyback off existing optical communications infrastructure, given that networking will almost inevitably be optically mediated. We have an existing intercontinental fibre-optic backbone, as well as sophisticated satellite networks. To what extent will this existing infrastructure (or future telecom/satellite infrastructure) be able to be exploited so as to avoid having to rebuild the entire future quantum internet infrastructure from scratch? This is a question worth billions of dollars. We also need to factor in that given the massive driving force behind telecom technology, its cost is following a Moore's Law-like trajectory of its own, and what costs a billion dollars today might cost a million dollars in a decade's time. In light of this, telecom wavelength quantum optics is being hotly pursued.

>>>>

A key question regarding the economics of the quantum internet is the extent to which it will be able to piggyback off existing optical communications infrastructure, given that networking will almost inevitably be optically mediated. We have an existing intercontinental fibre-optic backbone, as well as sophisticated satellite networks. To what extent will this existing infrastructure (or future telecom/satellite infrastructure) be able to be exploited so as to avoid having to rebuild the entire future quantum internet infrastructure from scratch? This is a question worth billions of dollars. We also need to factor in that given the massive driving force behind telecom technology, its cost is following a Moore's Law-like\index{Moore's Law} trajectory of its own, and what costs a billion dollars today might cost a million dollars in a decade's time. In light of this, telecom wavelength quantum optics is being hotly pursued.

### 2018-09-05 Sections/essay_the_era_of_quantum_supremacy.tex
Some proof-reading

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{moores_law}
\captionspacefig \caption{Historical trends in classical computing power for both PCs and top-end supercomputers, with an extrapolation 5 years into the future. The close fit to exponential growth in performance over time is apparent from the logarithmic scale.} \label{fig:moores_law}
\end{figure}

To put this into context, current day microprocessors contains on the order of billions of single transistors. Current day  experimental quantum computers, on the other hand, contain fewer than 100 qubits. We sit at the mere very beginning of Moore's adventure through the quantum era.

@@

While the power of classical computers scales at most linearly with the number of transistors, the classical-equivalent power\index{Classical-equivalent computational power} of quantum computers scales exponentially with the number of qubits (in the best-case scenario). The classical Moore's Law is close to saturation -- we simply can't make transistors too much smaller than they already are\footnote{Current transistor feature sizes are on the order of several hundred atoms. Under a Moore's Law prediction, we are likely to hit fundamental physical barriers in transistor size within a decade. We can't make a transistor smaller than an atom!}! We therefore envisage a new Quantum Moore's Law, which follows a far more impressive trajectory than its classical counterpart. The point of critical mass in quantum computing will take place when the classical and Quantum Moore's Law extrapolations intersect, signalling the commencement of the \textit{post-classical era}\index{Post-classical era}. Estimating this is more challenging than it sounds, since although the classical Moore's Law is extremely well established with an excellent fit to an exponential trajectory, there aren't yet enough data-points to make a confident prediction about a Quantum Moore's Law, to what trajectory it best fits, and at what rate it progresses.

>>>>

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{moores_law}
\captionspacefig \caption{Historical trends in classical computing power for both PCs and top-end supercomputers, with an extrapolation 5 years into the future. The close fit to consistent exponential growth in performance over time is apparent from the logarithmic scale.} \label{fig:moores_law}
\end{figure}

To put this into context, current day microprocessors contain on the order of billions of single transistors. Current day  experimental quantum computers, on the other hand, contain fewer than 100 qubits. We sit at the mere very beginning of Moore's adventure through the quantum era.

@@

While the power of classical computers scales at most linearly with the number of transistors, the classical-equivalent power\index{Classical-equivalent computational power} of quantum computers scales exponentially with the number of qubits (in the best-case scenario). The classical Moore's Law is close to saturation -- we simply can't make transistors too much smaller than they already are\footnote{Current transistor feature sizes are on the order of several hundred atoms. Under a Moore's Law prediction, we are likely to hit fundamental physical barriers in transistor size within a decade. We can't make a transistor smaller than an atom!}! We therefore envisage a new Quantum Moore's Law\index{Quantum Moore's Law}, which follows a far more impressive trajectory than its classical counterpart. The point of critical mass in quantum computing will take place when the classical and Quantum Moore's Law extrapolations intersect, signalling the commencement of the \textit{post-classical era}\index{Post-classical era} of \textit{quantum supremacy}\index{Quantum supremacy}. Estimating this is more challenging than it sounds, since although the classical Moore's Law is extremely well established with an excellent fit to an exponential trajectory, there aren't yet enough data-points to make a confident prediction about a Quantum Moore's Law, to what trajectory it best fits, and at what rate it progresses, not to mention unforeseeable black swans.

### 2018-09-05 Sections/essay_the_global_virtual_quantum_computer.tex
Some proof-reading

\subsection{The global virtual quantum computer} \label{sec:GVQC} \index{Virtual quantum computer}

From the quantum computational leverage phenomena\index{Quantum computational leverage} emerges an entirely new paradigm for future supercomputing. Rather than different quantum hardware vendors competing to have the biggest and best computers, using them independently in isolation, they are incentivised to unite their resources and leverage (`piggyback') off one another, to the (potentially exponential) benefit of all parties. The key observation is that \textit{all} network users gain positive leverage from other users joining the network, irrespective of their size.

Users who make an initial fixed investment into quantum computing infrastructure, which they contribute to the network, but are then unable or unwilling to finance further expansion of, will nonetheless observe exponential growth in their computing power over time. That is, the computational dividend yielded by a fixed investment increases exponentially over time. This creates a very powerful model for investment into computational infrastructure with no classical parallel, which could be particularly valuable in developing nations or less-wealthy enterprises.

@@

The leverage asymmetry will be a key consideration in answering this question, since although both parties benefit on an absolute basis from unification, on a relative basis the weaker party achieves the higher computational leverage. For this reason, it is plausible the global virtual quantum computer will fracture, dissolving into independent smaller virtual quantum computers, divided across geo-strategic boundaries, with the stronger parties seceding from the union -- the stronger nations, even though they would individually benefit computationally from unification, may not wish the weaker ones to piggyback off them, achieving greater leverage than themselves\footnote{Insert jokes about Greece and Germany here --- \textit{Im Wandel der Zeiten -- Eine Geschichte der Zivilisation.}}.

>>>>

\section{The global virtual quantum computer} \label{sec:GVQC} \index{Virtual quantum computer}

\dropcap{F}{rom} the uniquely quantum phenomena that computational power can scale exponentially with the size of a quantum computer, as opposed to the linear relationship observed in classical computing, emerges an entirely new paradigm for future supercomputing. Rather than different quantum hardware vendors competing to have the biggest and best computers, using them independently in isolation, they are incentivised to unite their resources over the network and leverage (`piggyback') off one another, forming a larger and exponentially more powerful \textit{virtual quantum computer}, which could then be time-shared between them, to the benefit of all parties. The key observation is that \textit{all} contributing users to the network gain leverage from other users unifying their assets, irrespective of their size. In fact, this computational leverage\index{Computational leverage} is greater for smaller contributors than larger ones, making the benefits of this phenomenon disproportionately benefit the less-well-resourced.

Users who make an initial fixed investment into quantum computing infrastructure, which they contribute to the network, but are then unable or unwilling to finance further expansion of, will nonetheless observe exponential growth in their computing power over time. That is, the computational dividend yielded by a fixed investment increases exponentially over time. This creates a very powerful economic model for investment into computational infrastructure with no classical parallel, which could be particularly valuable in developing nations or less-wealthy enterprises.

@@

The leverage asymmetry will be a key consideration in answering this question, since although both parties benefit on an absolute basis from unification, on a relative basis the weaker party achieves the higher computational leverage. For this reason, it is plausible the global virtual quantum computer will fracture, dissolving into independent smaller virtual quantum computers, divided across geo-strategic or competitive boundaries, with the stronger parties seceding from the union -- even though they would individually benefit computationally from unification, they may not wish the weaker ones to piggyback off them, achieving greater leverage than themselves\footnote{Insert jokes about Greece and Germany here --- \textit{Im Wandel der Zeiten -- Eine Geschichte der Zivilisation.}}.
